\begin{abstract}
Energy system optimization models are a class of tools designed to optimize
energy planning and are used by energy planners and decision-makers to generate
insights that inform energy policy. However, existing tools are challenged by
real-world scenarios which require optimization across multiple objectives. In
this paper, the multi-objective energy system optimization framework,
\texttt{Osier}, is demonstrated. \texttt{Osier} leverages genetic algortihms to
calculate a set of co-optimal solutions called a \textit{Pareto front}.
\texttt{Osier} also introduces a novel algorithm to identify a subset of
maximally different solutions within the sub-optimal space to address structural
uncertainty related to unmodeled objectives. By producing multiple solutions,
\texttt{Osier} gives modelers and decision-makers the tools to meaningfully
engage with public stakeholders and learn their preferences, thereby attending
to issues of procedural and recognition justice. This work verifies
\texttt{Osier}'s suitability for energy modeling problems with two \textit{in
silico} experiments. The first set of experiments compare \texttt{Osier} to a
more mature energy system optimization model, \texttt{Temoa}, to verify that
\texttt{Osier} produces results consistent with known methods. The results for a
least-cost optimization with \texttt{Osier} and \texttt{Temoa} show strong
agreement, within 0.5\% of each other. In the second, \texttt{Osier} reanalyzes
a set of nuclear fuel cycle options from the \texttt{SET} tool through the lens
of Pareto optimality. 
\end{abstract}
