\section{Introduction}

%% General Background
% The general background should demarcate the overall scientific setting of 
% your work. Start with a general topic that everyone in your audience cares 
% about. Note that the general background should give your audience a sense of 
% what to expect from your paper, not an overview of the history of a field. 
% Introduce only necessary background that is related to your work, and make 
% sure it can narrow down to your thesis.

%% Specific background: Work done so far
% Give your reader a sense of previous accomplishments, current contradictions, 
% and competing theories in the field. Cite previous work that illustrates your 
% narrative and gives a balanced description of the scientific landscape on 
% this research topic.  

%%  Knowledge gap: Motivation for your work Give 
% evidence of the incompleteness of the current understanding and of the value 
% of investigating the field further. What is the gap that needs to be filled? 
% Demonstrate the importance of this unsolved problem as the motivation for 
% your work.  2

%% Aim of your paper Finally, clearly state the aim and scope 
% of this article (not the project) and what exact question is answered. You 
% may also briefly explain how the study was conducted, and share a preview of 
% your findings.

Preventing the worst impacts of climate change will require our globalized society to transition from
fossil fuel infrastructure to clean energy infrastructure. This transition must
also be done equitably and justly to prevent entrenching further injustices to
marginalized and vulnerable communities. An economy-wide transition presents a
challenge unto itself due to the spatial, temporal, and topological complexities
of energy systems. Energy system optimization models (ESOMs) are a class of
tools designed to optimize this transition used by energy planners and
decision-makers to generate insights that inform policy. 

However, ESOMs have a few critical gaps. First, current ESOMs exclusively 
optimize on cost, yet real world decisions are also informed by non-financial 
priorities, such as sustainability and social benefits. Since these objectives 
cannot be neatly captured by a cost metric, ESOMs fail to optimize for these 
goals. Second, ESOMs struggle to meaningfully incorporate concepts of justice. 
Some studies model distributive justice --- related to the way benefits and 
burdens are shared among society's members --- but do so in an \textit{ex post} 
fashion. Procedural justice and recognition justice --- aspects of justice 
related to the policymaking process and context in which decisions are made --- 
are frequently sidelined. Indeed, ESOMs may be misused during a policymaking 
process to dismiss public input for lack of rigor. 

The aim of this paper This thesis attends to these 
flaws in ESOM tools by developing the first multi-objective energy system 
optimization framework, \texttt{Osier}.

Rather than returning a single optimal solution, multi-objective optimization
generates a set of co-optimal solutions called a \textit{Pareto front}, where no
objective can be improved without making another objective worse. The existence
of a Pareto front evinces tradeoffs which can only be resolved through dialogue
in a participatory process. \texttt{Osier} allows users to optimize arbitrarily
many objectives and define new objectives to create a bespoke, contextualized,
model. This thesis recognizes that some structural uncertainty will persist
regardless of the number of objectives. Thus, \texttt{Osier} leverages genetic
algorithms for their ability to sample complex Pareto fronts and because their
search methods automatically sample sub-optimal space. Further, this thesis
develops a novel algorithm to calculate a subset of maximally different
solutions within the sub-optimal space to address this uncertainty related to
unmodeled objectives. By producing multiple solutions, \texttt{Osier} gives
modelers and decision-makers the tools to meaningfully engage with public
stakeholders and learn their preferences, thereby attending to issues of
procedural and recognition justice.

This thesis verified \texttt{Osier}'s suitability for energy modeling problems
with several \textit{in silico} experiments. The first set of experiments demonstrate that
\texttt{Osier} produces results that are internally consistent within its suite
of available methods. The next set of experiments compare \texttt{Osier} to a
more mature ESOM, \texttt{Temoa}, to verify that \texttt{Osier} produces results
consistent with known methods. The results for a least-cost optimization with
\texttt{Osier} and \texttt{Temoa} show strong agreement, with 0.5\% of each
other. In addition to benchmarking exercises, this thesis applies \texttt{Osier}
to two timely examples. The first uses \texttt{Osier} to reanalyze a set of
nuclear fuel cycle options through the lens of Pareto optimality. The second
shows how \texttt{Osier} optimizes a novel objective,
energy-return-on-investment, for a hypothetical data center. Finally, this
thesis validates earlier claims of \texttt{Osier}'s usefulness for energy
planning through a qualitative study of municipal and state-level energy
planners in Illinois. The results of thirteen expert interviews demonstrate
enthusiasm for a new tool that can optimize objectives beyond cost. However,
this study surfaced structural barriers to ESOM usage at the municipal level
which must be addressed before ESOMs, like \texttt{Osier}, can be adopted.
Lastly, I recommend that the state of Illinois develop a participatory process
for its energy modeling exercises

